---
title: 'Assignment #1'
author: "Tianqi Wang"
date: "September 18, 2016"
output: word_document
---
create a uniform distribution 
```{r}
set.seed(1234567)      
unif<- runif(1000000) #get a uniform distribution of one million numbers
hist(unif)            
summary(unif)       
```








run 1,000 instances of each sample size and calculate the mean of different sizes
```{r}

  numSamples=1000                 # num of samples - not size of sample
  ubsamp=c(1:numSamples)          # create the vector (array)
  for (n in c(2:4)){                         # 3 different sample sizes
    for (repeats in c(1:numSamples)){        # numSamples instances of each size
        number=n*10^(n-1)                          # size=20, 300, and 4,000
        ubsamp[repeats]=mean(sample(unif,size=number,replace=TRUE))
                                             # fill in a vector with 1,000 entries
                                             # each of which is the mean of sample
                                        
        }
    line=paste0("sample size is ",  number,  " and sample mean is " , 
                mean(ubsamp))
                                             # edit text and numbers together in
                                             # one line
    print (line)                             # and print it out.
  }
```







create a biased section of different sizes and run 1,000 instances of each sample size and calculate the mean 
```{r}
               
  numSamples=1000
  ubsamp=c(1:numSamples)
  for (n in c(2:4)){                         # 3 different sample sizes
    for (repeats in c(1:numSamples)){        # numSamples instances of each size
        number=n*10^(n-1)                          # size=20, 300, and 4,000
        thisSample=c(1:number)
        thisSample=sample(unif,size=number,replace=TRUE)
        for (thisOne in c(1:number)){
          if (thisSample[thisOne]>0.6&thisSample[thisOne]<0.7) thisSample[thisOne]=NA           
        }
        ubsamp[repeats]=mean(thisSample,na.rm=TRUE)
                                             # fill in a vector with 1,000 entries
                                             # each of which is the mean of sample
        }
    line=paste0("sample size is ",  number,  " and sample mean is " , 
                mean(ubsamp))
                                             # edit text and numbers together in
                                             # one line
    print (line)                             # and print it out.
  }
```



```{r}
mean(unif)
sd(unif)
```







run 1,000 instances of each sample size and plot the mean of different size
```{r}
for (i in c(2:4)){
  number=i*10^(i-1)
  samplevector=c(1:1000)
  for (j in c(1:1000)){
    samplevector[j]=mean(sample(unif,size=number,replace=TRUE))
    }
  
  if (i==2) {
    hist(samplevector,col="red")
  }
  if (i==3) {
    hist(samplevector,add=T,col="green")
  }
  if (i==4) {
    hist(samplevector,add=T,col="Black")
  }

  print (paste0("sample size is ", number, " and sd is ", sd(samplevector)))
}
```








optional:


run 1,000 instances of each sample size,plot the standard deviation of different sizes and caculate the different from standard deviation
```{r}
popsd=sd(unif)
for (i in c(2:4)){
  number=i*10^(i-1)
  samplevector=c(1:1000)
  for (j in c(1:1000)){
    samplevector[j]=sd(sample(unif,size=number,replace=TRUE))
    }
  
  if (i==2) {
    hist(samplevector,col="red")
  }
  if (i==3) {
    hist(samplevector,add=T,col="green")
  }
  if (i==4) {
    hist(samplevector,add=T,col="Black")
  }

  print (paste0("sample size is ", number, " and abs diff from sd is ", abs(popsd-mean(samplevector))))
}
```
